### 2022-05-12 supplement.Rmd
Re-order supplementary tables

@@

@@

  # Combine two-level, trim-and-fill, and selection models
  tibble(
    res = c(
      list(
        res_freq_2_lvl[[name]],
        res_trim_fill[[name]],
        res_selection_weights[[name]]
      ),
      res_selection_steps[[name]]
    ),
    label_1 = c(
      "Two-level model", "Trim-and-fill model",
      "Selection models:", "", "", "", ""
    ),
    label_2 = c(
      "", "", "Weight function [.01, .05, .30]",
      "One-tailed, moderate bias", "One-tailed, severe bias",
      "Two-tailed, moderate bias", "Two-tailed, severe bias"
    )
  ) %>%
    # Combine and format as a table
    pmap_dfr(
      ~ print_res_freq_table(
        res_freq = ..1, label_1 = ..2, label_2 = ..3,
        label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
      )
    ) %>%
    select(-Parameter) %>%
    rename(`Hedges' $g$` = Estimate)
}) %>%
  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection

```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5}
# Create new funnel plots that take the trim-and-fill results into account
map2(res_trim_fill, plots_funnel, function(res, plot) {

@@

>>>>

```{r, primsa_checklist, include=TRUE}
# Read the CSV file
tab_prisma <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "cic"
)

# Display the table
apa_table(
  tab_prisma,
  align = "lcl",
  caption = "PRISMA 2020 checklist",
  font_size = "scriptsize"
)
```

@@

  # Combine two-level, trim-and-fill, and selection models
  tibble(
    res = c(
      list(
        res_freq_2_lvl[[name]],
        res_trim_fill[[name]],
        res_selection_weights[[name]]
      ),
      res_selection_steps[[name]]
    ),
    label_1 = c(
      "Two-level model", "Trim-and-fill model",
      "Selection models", "", "", "", ""
    ),
    label_2 = c(
      "--", "--", "Weight function [.01, .05, .30]",
      "One-tailed, moderate bias", "One-tailed, severe bias",
      "Two-tailed, moderate bias", "Two-tailed, severe bias"
    )
  ) %>%
    # Combine and format as a table
    pmap_dfr(
      ~ print_res_freq_table(
        res_freq = ..1, label_1 = ..2, label_2 = ..3,
        label_col_1 = "Model", label_col_2 = "Sub-model", print_sigma2s = FALSE
      )
    ) %>%
    select(-Parameter) %>%
    rename(`Hedges' $g$` = Estimate)
}) %>%
  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection

@@

```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5, fig.cap="(ref:figs4-caption)"}
# Create new funnel plots that take the trim-and-fill results into account
map2(res_trim_fill, plots_funnel, function(res, plot) {

@@

(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance **(a)** and in the meta-analysis of gender differences within each article **(b)**. The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines). Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis. Red squares show (fictional) experiments that were imputed via the trim-and-fill analyses, compensating for the small publication bias observed in the original funnel plots. Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses.
